Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-06-20 paper.tex
yea

A 10ppm precursor mass tolerance is used for the initial calibration step, and then reduced to 5ppm for subsequent searches.
We allowed 120 modifications including PTMs, adducts, and chemical modifications in the database augmentation step.
%Final notch search used notches centered at \{0, 1.0029, 2.0052, 3.0077\} in order to capture missed identifications due to missed monoisotopic peaks.

@@

@@

The final search with the augmented database is conducted with notches: we only recommend including the common missed monoisotopic mass values in the final search,.
The effect of using these notches is shown in Table~\ref{tab:table2}.

@@

The initial notch search is significantly faster than a corresponding wide mass search, and this suggests that multiple search rounds could be conducted, iteratively adding more and more modifications.
This recursive nature of the algorithm is well suited to add multiple modifications of different types on the same peptide.
Due to these enhancements, we test the performance of our methods

\begin{table}[]
\centering
\caption{My caption}
\label{my-label}
\begin{tabular}{|l|l|l|l|l|l|}
\hline
                      &        & \multicolumn{2}{l|}{Single Round}                                                                              & \multicolumn{2}{l|}{Multiple Rounds}                                                                           \\ \hline
                      &        & \begin{tabular}[c]{@{}l@{}}Mods:\\ none\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ ptmlist\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ none\end{tabular} & \begin{tabular}[c]{@{}l@{}}Mods:\\ ptmlist\end{tabular} \\ \hline
\multirow{2}{*}{PSMs} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\multirow{2}{*}{Mods} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\multirow{2}{*}{Time} & Jurkat &                                                      &                                                         &                                                      &                                                         \\ \cline{2-6} 
                      & Mouse  &                                                      &                                                         &                                                      &                                                         \\ \hline
\end{tabular}
\end{table}

\subsection{Discovery of Modifications not in Database}

>>>>

A 10ppm precursor mass tolerance is used for the initial calibration step, and then reduced to 5ppm for subsequent searches.
We allowed 120 modifications including PTMs, adducts, and chemical modifications in the database augmentation step.

@@

\subsubsection{Discovery of Modifications not in Database}

@@

The final notch search uses notches centered at \{0, 1.0029, 2.0052, 3.0077\}, in order to capture missed identifications due to missed monoisotopic peaks.
The results are contrasted with the standard narrow-mass final search.
The effect of using these notches is shown in Table~\ref{tab:table2}.

@@
